---
title: "Vignette for Package simplin"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{simp_lin}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

$\texttt{simplin}$ provides a function for fast simple linear regression. The package includes two functions $\texttt{sim_lin_R}$ and $\texttt{sim_lin}$. $\texttt{sim_lin}$ is written in $\texttt{Rcpp}$ and intakes two numeric vectors and outputs, in a list, point estimates, standard errors, and 95% confidence intervals for the regression parameters $\beta_0$ and $\beta_1$ as well as the predicted values ($\mathbf{\hat{y}}$) and residuals ($\mathbf{e_i}=\mathbf{y}-\mathbf{\hat{y}}$). $\texttt{sim_lin_R}$ is an $R$ function that checks if input vectors are numeric and of the same length before calling $\texttt{sim_lin}$. 

# Implementation 

```{r setup}
### Load package
library(simplin)

### Simulate Data
x = rnorm(10)
y = x + rnorm(10)

### Fit Simple Linear Regression Model
output <- simp_lin_R(x,y)

### Point Estimates, order beta_0, beta_1
output$Point.Estimates

### Standard Errors
output$Standard.Error

### 95% Confidence Intervals
output$`CI_95%s`

### Predicted Values
output$Predictions

### Residuals 
output$Residuals
```
